Chapter 3: Appendix

### 2021-03-23 appendix_chapter_3.Rmd
changed mean traj plots

# Appendix

## Domain features

```{r eval=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE, eval=FALSE}

library(jpeg)
library(grid)
library(gridExtra)

vector_2 <- rasterGrob(as.raster(readJPEG("OceanParcels/trajectory_data/vector_outputs/jpeg/vector_day2.jpg")))
vector_5 <- rasterGrob(as.raster(readJPEG("OceanParcels/trajectory_data/vector_outputs/jpeg/vector_day5.jpg")))
vector_10 <- rasterGrob(as.raster(readJPEG("OceanParcels/trajectory_data/vector_outputs/jpeg/vector_day10.jpg")))
vector_15 <- rasterGrob(as.raster(readJPEG("OceanParcels/trajectory_data/vector_outputs/jpeg/vector_day15.jpg")))
vector_20 <- rasterGrob(as.raster(readJPEG("OceanParcels/trajectory_data/vector_outputs/jpeg/vector_day20.jpg")))
vector_25 <- rasterGrob(as.raster(readJPEG("OceanParcels/trajectory_data/vector_outputs/jpeg/vector_day25.jpg")))
vector_30 <- rasterGrob(as.raster(readJPEG("OceanParcels/trajectory_data/vector_outputs/jpeg/vector_day30.jpg")))

ggarrange(vector_2, vector_5, vector_10, vector_15, vector_20, vector_25, vector_30, labels = "AUTO")
```

## Additional comparisons

@@

p_RK4_April$type <- "RK4_April" # add extra column 'type' to dataframe and assigned 'RK4' label

@@

Min_Kfloat_H100_W00_April$type <- "Min_Kfloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_April$velocity <- with(Min_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05_April$type <- "Min_Kfloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_April$velocity <- with(Min_Kfloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10_April$type <- "Min_Kfloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_April$velocity <- with(Min_Kfloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15_April$type <- "Min_Kfloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_April$velocity <- with(Min_Kfloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00_April$type <- "Mean_Kfloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_April$velocity <- with(Mean_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05_April$type <- "Mean_KFloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_April$velocity <- with(Mean_KFloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10_April$type <- "Mean_KFloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_April$velocity <- with(Mean_KFloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15_April$type <- "Mean_KFloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_April$velocity <- with(Mean_KFloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00_April$type <- "Max_KFloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_April$velocity <- with(Max_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05_April$type <- "Max_KFloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_April$velocity <- with(Max_Kfloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10_April$type <- "Max_KFloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_April$velocity <- with(Max_Kfloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15_April$type <- "Max_KFloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_April$velocity <- with(Max_Kfloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))

@@

p_RK4_July$type <- "RK4_July" # add extra column 'type' to dataframe and assigned 'RK4' label

@@

Min_Kfloat_H100_W00_July$type <- "Min_Kfloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_July$velocity <- with(Min_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05_July$type <- "Min_Kfloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_July$velocity <- with(Min_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10_July$type <- "Min_Kfloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_July$velocity <- with(Min_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15_July$type <- "Min_Kfloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_July$velocity <- with(Min_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00_July$type <- "Mean_Kfloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_July$velocity <- with(Mean_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05_July$type <- "Mean_KFloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_July$velocity <- with(Mean_KFloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10_July$type <- "Mean_KFloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_July$velocity <- with(Mean_KFloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15_July$type <- "Mean_KFloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_July$velocity <- with(Mean_KFloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00_July$type <- "Max_KFloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_July$velocity <- with(Max_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05_July$type <- "Max_KFloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_July$velocity <- with(Max_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10_July$type <- "Max_KFloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_July$velocity <- with(Max_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15_July$type <- "Max_KFloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_July$velocity <- with(Max_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

p_RK4_Oct$type <- "RK4_Oct" # add extra column 'type' to dataframe and assigned 'RK4' label

@@

Min_Kfloat_H100_W00_Oct$type <- "Min_Kfloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_Oct$velocity <- with(Min_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05_Oct$type <- "Min_Kfloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_Oct$velocity <- with(Min_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10_Oct$type <- "Min_Kfloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_Oct$velocity <- with(Min_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15_Oct$type <- "Min_Kfloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_Oct$velocity <- with(Min_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00_Oct$type <- "Mean_Kfloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_Oct$velocity <- with(Mean_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05_Oct$type <- "Mean_KFloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_Oct$velocity <- with(Mean_KFloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10_Oct$type <- "Mean_KFloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_Oct$velocity <- with(Mean_KFloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15_Oct$type <- "Mean_KFloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_Oct$velocity <- with(Mean_KFloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00_Oct$type <- "Max_KFloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_Oct$velocity <- with(Max_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05_Oct$type <- "Max_KFloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_Oct$velocity <- with(Max_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10_Oct$type <- "Max_KFloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_Oct$velocity <- with(Max_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15_Oct$type <- "Max_KFloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_Oct$velocity <- with(Max_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

```{r, message=FALSE, echo=FALSE, warning=FALSE}
waterdrag_plot_April <- ggplot()+
  #geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_April, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_April, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_April, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean_April, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  #geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_April, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean_April, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean_April, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean_April, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean_April, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean_April, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean_April, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean_April, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean_April, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean_April, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

>>>>

# Appendix
## Additional comparisons

@@

p_RK4_April$type <- "RK4_April" # add extra column 'type' to dataframe and assigned 'RK4' label
p_RK4_mean_April$type <- "17" # add extra column 'type' to dataframe and assigned 'RK4' label

@@

Min_Kfloat_H100_W00_April$type <- "Min_Kfloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_April$velocity <- with(Min_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H100_W00_mean_April$type <- "18" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H095_W05_April$type <- "Min_Kfloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_April$velocity <- with(Min_Kfloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H095_W05_mean_April$type <- "19" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H090_W10_April$type <- "Min_Kfloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_April$velocity <- with(Min_Kfloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H090_W10_mean_April$type <- "20" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H085_W15_April$type <- "Min_Kfloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_April$velocity <- with(Min_Kfloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H085_W15_mean_April$type <- "21" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_Kfloat_H100_W00_April$type <- "Mean_Kfloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_April$velocity <- with(Mean_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_Kfloat_H100_W00_mean_April$type <- "22" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H095_W05_April$type <- "Mean_KFloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_April$velocity <- with(Mean_KFloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H095_W05_mean_April$type <- "23" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H090_W10_April$type <- "Mean_KFloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_April$velocity <- with(Mean_KFloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H090_W10_mean_April$type <- "24" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H085_W15_April$type <- "Mean_KFloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_April$velocity <- with(Mean_KFloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H085_W15_mean_April$type <- "25" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H100_W00_April$type <- "Max_KFloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_April$velocity <- with(Max_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H100_W00_mean_April$type <- "26" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H095_W05_April$type <- "Max_KFloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_April$velocity <- with(Max_Kfloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H095_W05_mean_April$type <- "27" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H090_W10_April$type <- "Max_KFloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_April$velocity <- with(Max_Kfloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H090_W10_mean_April$type <- "28" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H085_W15_April$type <- "Max_KFloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_April$velocity <- with(Max_Kfloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H085_W15_mean_April$type <- "29" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

p_RK4_July$type <- "RK4_July" # add extra column 'type' to dataframe and assigned 'RK4' label
p_RK4_mean_July$type <- "30" # add extra column 'type' to dataframe and assigned 'RK4' label

@@

Min_Kfloat_H100_W00_July$type <- "Min_Kfloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_July$velocity <- with(Min_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H100_W00_mean_July$type <- "31" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H095_W05_July$type <- "Min_Kfloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_July$velocity <- with(Min_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H095_W05_mean_July$type <- "32" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H090_W10_July$type <- "Min_Kfloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_July$velocity <- with(Min_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H090_W10_mean_July$type <- "33" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H085_W15_July$type <- "Min_Kfloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_July$velocity <- with(Min_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H085_W15_mean_July$type <- "34" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_Kfloat_H100_W00_July$type <- "Mean_Kfloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_July$velocity <- with(Mean_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_Kfloat_H100_W00_mean_July$type <- "35" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H095_W05_July$type <- "Mean_KFloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_July$velocity <- with(Mean_KFloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H095_W05_mean_July$type <- "36" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H090_W10_July$type <- "Mean_KFloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_July$velocity <- with(Mean_KFloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H090_W10_mean_July$type <- "37" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H085_W15_July$type <- "Mean_KFloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_July$velocity <- with(Mean_KFloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H085_W15_mean_July$type <- "38" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H100_W00_July$type <- "Max_KFloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_July$velocity <- with(Max_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H100_W00_mean_July$type <- "39" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H095_W05_July$type <- "Max_KFloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_July$velocity <- with(Max_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H095_W05_mean_July$type <- "40" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H090_W10_July$type <- "Max_KFloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_July$velocity <- with(Max_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H090_W10_mean_July$type <- "41" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H085_W15_July$type <- "Max_KFloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_July$velocity <- with(Max_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H085_W15_mean_July$type <- "42" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

p_RK4_Oct$type <- "RK4_Oct" # add extra column 'type' to dataframe and assigned 'RK4' label
p_RK4_mean_Oct$type <- "43" # add extra column 'type' to dataframe and assigned 'RK4' label

@@

Min_Kfloat_H100_W00_Oct$type <- "Min_Kfloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_Oct$velocity <- with(Min_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H100_W00_mean_Oct$type <- "44" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H095_W05_Oct$type <- "Min_Kfloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_Oct$velocity <- with(Min_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H095_W05_mean_Oct$type <- "45" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H090_W10_Oct$type <- "Min_Kfloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_Oct$velocity <- with(Min_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H090_W10_mean_Oct$type <- "46" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Min_Kfloat_H085_W15_Oct$type <- "Min_Kfloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_Oct$velocity <- with(Min_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Min_Kfloat_H085_W15_mean_Oct$type <- "47" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_Kfloat_H100_W00_Oct$type <- "Mean_Kfloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_Oct$velocity <- with(Mean_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_Kfloat_H100_W00_mean_Oct$type <- "48" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H095_W05_Oct$type <- "Mean_KFloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_Oct$velocity <- with(Mean_KFloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H095_W05_mean_Oct$type <- "49" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H090_W10_Oct$type <- "Mean_KFloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_Oct$velocity <- with(Mean_KFloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H090_W10_mean_Oct$type <- "50" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Mean_KFloat_H085_W15_Oct$type <- "Mean_KFloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_Oct$velocity <- with(Mean_KFloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Mean_KFloat_H085_W15_mean_Oct$type <- "51" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H100_W00_Oct$type <- "Max_KFloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_Oct$velocity <- with(Max_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H100_W00_mean_Oct$type <- "52" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H095_W05_Oct$type <- "Max_KFloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_Oct$velocity <- with(Max_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H095_W05_mean_Oct$type <- "53" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H090_W10_Oct$type <- "Max_KFloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_Oct$velocity <- with(Max_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H090_W10_mean_Oct$type <- "54" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

Max_Kfloat_H085_W15_Oct$type <- "Max_KFloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_Oct$velocity <- with(Max_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))
Max_Kfloat_H085_W15_mean_Oct$type <- "55" # add extra column 'type' to dataframe and assigned 'kelp' label

@@

```{r, message=FALSE, echo=FALSE, warning=FALSE}

total_mean_water_April <- rbind(p_RK4_mean_April, Min_Kfloat_H100_W00_mean_April, Mean_Kfloat_H100_W00_mean_April, Max_Kfloat_H100_W00_mean_April)
total_mean_ww_April <- rbind(p_RK4_mean_April, Min_Kfloat_H095_W05_mean_April, Min_Kfloat_H090_W10_mean_April, Min_Kfloat_H085_W15_mean_April, Mean_KFloat_H095_W05_mean_April, Mean_KFloat_H090_W10_mean_April, Mean_KFloat_H085_W15_mean_April, Max_Kfloat_H095_W05_mean_April, Max_Kfloat_H090_W10_mean_April, Max_Kfloat_H085_W15_mean_April)

total_mean_water_April$type <- factor(total_mean_water_April$type, levels=c("17", "18", "22", "26"))
total_mean_ww_April$type <- factor(total_mean_ww_April$type, levels=c("17", "19", "20", "21", "23", "24", "25", "27", "28", "29"))

waterdrag_plot_April <- ggplot()+
  #geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = total_mean_water_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  #geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = total_mean_ww_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

total_mean_water_July <- rbind(p_RK4_mean_July, Min_Kfloat_H100_W00_mean_July, Mean_Kfloat_H100_W00_mean_July, Max_Kfloat_H100_W00_mean_July)
total_mean_ww_July <- rbind(p_RK4_mean_July, Min_Kfloat_H095_W05_mean_July, Min_Kfloat_H090_W10_mean_July, Min_Kfloat_H085_W15_mean_July, Mean_KFloat_H095_W05_mean_July, Mean_KFloat_H090_W10_mean_July, Mean_KFloat_H085_W15_mean_July, Max_Kfloat_H095_W05_mean_July, Max_Kfloat_H090_W10_mean_July, Max_Kfloat_H085_W15_mean_July)

total_mean_water_July$type <- factor(total_mean_water_July$type, levels=c("30", "31", "35", "39"))
total_mean_ww_July$type <- factor(total_mean_ww_July$type, levels=c("30", "32", "33", "34", "36", "37", "38", "40", "41", "42"))
